Tight Generalization Bounds for Hard Parameter Sharing in High-dimensional Linear Regression

### 2020-10-18 arxiv/proof_same_cov.tex
section A B

	Our next claim shows that the subspace spanned by the rows of $\hat{A}$ is close to that of $A^{\star}$.
	\begin{claim}\label{claim_opt_dist}
		Let $U_{\hat{A}} U_{\hat{A}}^{\top} \in\real^{t\times t}$ denote the subspace projection $\hat{A}^{\top} (\hat{A}\hat{A}^{\top})^{+} \hat{A}$.
		In the setting of Theorem \ref{thm_many_tasks}, we have that
		\[ \bignormFro{U_{\hat{A}} U_{\hat{A}}^{\top} - A^{\star} {A^{\star}}^{\top}}^2
				\le  n^{-c_{\varphi}} \cdot \frac{t(  \bignorm{\Sigma^{1/2} B^{\star}}^2 +  \sigma^2 )}{\lambda_r- \lambda_{r+1}}. \]
	\end{claim}
	The proof of the above claim is based on the following characterization.

@@

	The next piece of our proof deals with the prediction loss of hard parameter sharing.
	\begin{claim}\label{claim_pred_err}
		In the setting of Theorem \ref{thm_many_tasks},
		let $\hat{a}_i = \hat{A}^{\top} (\hat{A}\hat{A}^{\top})^{+} \hat{A}_i$.
		We have that the prediction loss of $\hat{\beta}_i^{\MTL} := \hat{B} \hat{A}_i$ satisfies that
		\begin{align*}
			\bigabs{L(\hat{\beta}_i^{\MTL}) - L(B^{\star} \hat{a}_i) - \sigma^2 \norm{\hat{a}_i}^2 \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}}
			\le  n^{-1/4} \left(\|\Sigma^{1/2}B^{\star} \|^2+ \sigma^2  \cdot\|\hat a_i\|^2\right) .
		\end{align*}
	\end{claim}
	%The proof of Claim \ref{claim_opt_dist}, Claim \ref{lem_exp_opt}, and Claim \ref{claim_pred_err} can be found in Appendix \ref{app_proof_error_same_cov}.
	Provided with these results, we are ready to prove Theorem \ref{thm_many_tasks}.
	\begin{proof}[Proof of Theorem \ref{thm_many_tasks}]
		Using Claim \ref{claim_pred_err}, we get that the prediction loss of $\hat{\beta}_i^{\MTL}$ is equal to  $L(B^{\star}\hat{a}_i)+\sigma^2\norm{\hat{a}_i}^2\cdot \bigtr{\Sigma(X^{\top}X)^{-1}}$ up to a small enough error. Moreover, Claim \ref{claim_opt_dist} gives directly an upper bound on $\|\hat a_i - a_i^\star\|^2$. With this estimate, we can bound the difference
		$$L(B^{\star}\hat{a}_i)+\sigma^2\norm{\hat{a}_i}^2\cdot \bigtr{\Sigma(X^{\top}X)^{-1}} - L(B^{\star} {a}^\star_i)-\sigma^2\norm{{a}^\star_i}^2\cdot \bigtr{\Sigma(X^{\top}X)^{-1}}.$$
		Combined together, our proof is complete. We omit the details.
%		For the latter, we use Claim \ref{claim_opt_dist} to upper bound the difference between $\norm{\hat{a}_i}^2$ and $\norm{a_i^{\star}}^2$.
%		For $L(B^{\star}\hat{a}_i)$, we again use Claim \ref{claim_opt_dist} to upper bound the distance between $\hat{a}_i$ and $a_i^{\star}$.
%		Combined together, our proof is complete.
	\end{proof}

@@

	\paragraph{Part 3:} The last part is the square of $E_j$:
	\begin{align}\label{eq_gA_p3}
		\sum_{j=1}^t \norm{E_j}^2 &= \bignormFro{\cW A - \cE}^2
		= \bignormFro{\cE}^2 - \inner{\cW A}{\cE},
	\end{align}
	where in the second step we used $\norm{\cW A}^2 = \inner{\cW A}{\cE}$ by algebraic calculation.
	Hence, it suffices to show that the expectation of equation \eqref{eq_gA_p3} is equal to $\sigma^2 (n\cdot t - p\cdot r)$.
	First, we have that $\ex{\|\cE\|_F^2} = \sigma^2 \cdot n \cdot t$.
%	Conditional on $X$, we have that
%	\begin{align*}
%		\exarg{\cE}{\norm{E_j}^2}
%		= \exarg{\cE}{\sum_{j=1}^t \bigbrace{\bignorm{\cW A_j}^2 - 2\inner{\cW A_j}{\varepsilon^{(j)}} }} + \sigma^2 \cdot n \cdot t.
%	\end{align*}
%	We consider both terms in the above equation one by one.
	Second, notice that for the subspace projection $U_XU_X^\top:=X(X^{\top} X)^{-1} X^{\top}$ and $1\le i, j \le t$,
	%\begin{align}
	%	\sum_{j=1}^t \norm{\cW A_j}^2 = \sum_{j=1}^t \bigtr{\cW A_j A_j^{\top} \cW^{\top}} = \bigtr{\cW AA^{\top} \cW^{\top}} = \bigtr{U_X U_X^{\top} \cE A^{\top} (AA^{\top})^{-1} A \cE^{\top}}. \label{eq_proof_same_cov_1}
	%\end{align}
	%We observe that
	\begin{align*}
			 \exarg{\cE}{(\cE^{\top}U_XU_X^\top \cE)_{ij} }
		&= \exarg{\cE}{{\varepsilon^{(i)}}^\top U_X U_X^\top  \varepsilon^{(j)} } = \sigma^2 \cdot \tr\left( U_XU_X^\top \right) \cdot \delta_{ij} = p\sigma^2 \cdot \delta_{ij},
	\end{align*}
	which implies that $\exarg{\cE}{\cE^{\top}U_XU_X^\top \cE }=p\sigma^2 \cdot \id_{t\times t}$.
	Above, the second step used the fact that $\E(\varepsilon^{(i)}_k \varepsilon^{(i)}_l )=\sigma^2\cdot \delta_{ij}\delta_{kl}$ for $1\le k,l \le n$, and the third step used the fact that $\tr(U_XU_X^\top) =\tr(U_X^\top U_X) =p$.
	Therefore, we have that
%	\begin{align*}
%		\inner{\cW A}{\cE} = \sigma^2 \cdot r \cdot \bigtr{U_X U_X^{\top}} = \sigma^2 \cdot r \cdot p,
%	\end{align*}
%because $U_X$ has rank $p$ by Fact \ref{lem_minv}.
	\begin{align*}
		\exarg{\cE}{ \inner{\cW A}{\cE}} =\E \bigtr{\cal E^\top U_X U_X^\top \cal E U_AU_A^\top}= p\sigma^2 \cdot \bigtr{ U_AU_A^\top} =  p \sigma^2 \cdot r ,
			\end{align*}
   because $U_AU_A^\top$ has rank $r$.	
	%Next, note that
	%\[ \sum_{j=1}^t \inner{\cW A_j}{\varepsilon^{(j)}} = \bigtr{\cW A\cE^{\top}}, \]
	%which is equal to equation \eqref{eq_proof_same_cov_1} by the definition of $\cW$.

	Combining the above three parts, the proof of Claim \ref{lem_exp_opt} is completed.
	\end{proof}

@@

	\begin{proof}[Proof of Claim \ref{claim_opt_dist}]
	Corresponding to the right-hand side of \eqref{eq_gA}, we define the function
	\be\label{same_hA}h(A):= n \bignormFro{\Sigma^{1/2} B^{\star} \bigbrace{A^{\top} (AA^{\top})^{+} A - \id_{t\times t}}}^2 + \sigma^2 (n\cdot t - p \cdot r).\ee
	In order to show that the $U_{\hat{A}}U_{\hat{A}}^\top$ is close to $A^\star {A^\star}^\top$, we first show that $g(A)$ is close to $h(A)$ as follows:
	\begin{align}\label{eq_gA_err}
		\bigabs{g(A) - h(A)} \lesssim  n^{-c_{\varphi}} \cdot n \bignorm{\Sigma^{1/2} B^{\star} (U_AU_A^{\top} - \id_{t\times t})}^2 + n^{-c_{\infty}} \cdot \sigma^2 \cdot n \cdot t,
	\end{align}
	for any fixed values $c_{\varphi}$ within $(0, \frac{\varphi-4}{2\varphi})$ and $c_{\infty}$ within $(0, 1/2)$. 
%	\begin{align}\label{eq_gA_err}
%		\bigabs{g(A) - \exarg{\cE, X}{g(A)}} \lesssim p^{-c_{\varphi}} \cdot n \bignorm{\Sigma^{1/2} B^{\star} (U_AU_A^{\top} - \id)}^2 + p^{-c_{\infty}} \cdot \sigma^2 \cdot n \cdot t.
%	\end{align}
	To show the above result, we consider the concentration error of each part of $g(A)$.

	For equation \eqref{eq_gA_p1}, % $g_0(\cal W)= \sum_{j=1}^t\left\|Z v_j \right\|^2$.
%	$$g_0(\cal W)= \sum_{j=1}^t\left\|Z v_j \right\|^2,\quad v_j:= \Sigma^{1/2}\left(B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j -  \beta_j\right).$$
%	note that $X H_j = Z \Sigma^{1/2} H_j \in \real^n$ is a random vector with i.i.d. entries of mean zero, variance $\|\Sigma^{1/2}H_j\|^2$, and finite $\varphi$-th moment by Assumption \eqref{assume_rm}.
%	Hence by the law of large numbers, we have that with high probability	
	applying Corollary \ref{cor_largedeviation} to $X H_j = Z \Sigma^{1/2} H_j$, we obtain that 
	${\left\|Z \Sigma^{1/2} H_j \right\|^2 } = { n \|\Sigma^{1/2} H_j\|^2} \cdot (1 + \OO(n^{-c_\varphi}))$ with high probability. 
	%, for a small enough constant $\e$,
	This implies that
	\begin{align}
		\abs{\sum_{j=1}^t \|X H_j\|^2 -  \sum_{j=1}^t n\norm{\Sigma^{1/2} H_j}^2} \lesssim   n^{-c_{\varphi}} \cdot n  \bignorm{\Sigma^{1/2} B^{\star} (U_{A}U_A^{\top} - \id_{t\times t})}^2. \label{eq_gA_err1}
	\end{align}

	For equation \eqref{eq_gA_p2}, 
	%using Lemma \ref{largedeviation} in Appendix \ref{app_tool} and the fact that all moments of $\varepsilon_i$ exist by Assumption \eqref{assmAhigh2}, 
	using Corollary \ref{cor_calE}, we obtain the following with high probability for any small constant $\e>0$:
	\begin{align}
		|\inner{XB^{\star} (U_AU_A^{\top} - \id_{t\times t})}{\cE}| &\le n^\e \cdot \sigma \cdot \bignormFro{XB^{\star} (U_AU_A^{\top} - \id_{t\times t})} \nonumber \\
		&\le n^{\e} \cdot \sigma \cdot \norm{Z} \cdot \bignormFro{\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id_{t\times t})} \nonumber \\
		&\lesssim n^{\e} \cdot \sigma \cdot \sqrt{n}\cdot \sqrt{t}\bignorm{\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id_{t\times t})} \nonumber \\
		&\le  n^{c_\infty +c} \cdot \bignorm{\Sigma^{1/2} B^{\star} (U_AU_A^{\top} - \id_{t\times t})}^2 + n^{-c_{\infty}} \cdot \sigma^2 \cdot n \cdot t,
		\label{eq_gA_err2}
	\end{align}
	which is bounded by the right hand side of equation \eqref{eq_gA_err} as long as $c$ is sufficiently small.
	In the second step, we used the fact that $X=Z\Sigma^{1/2}$.
	In the third step, we used Fact \ref{fact_minv} (ii) to bound the operator norm $\|Z\|$ by $\OO(\sqrt{n})$, and used $\bignormFro{\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id_{t\times t})}\le \sqrt{t} \bignorm{\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id_{t\times t})}$ since the matrix $\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id_{t\times t})$ has rank at most $t$. In the fourth step, we used AM-GM inequality.

	For equation \eqref{eq_gA_p3}, using Corollary \ref{cor_calE},
	%Lemma \ref{largedeviation} and the fact that all moments of $\varepsilon_i$ exist, 
	we obtain that with high probability,
	\begin{align}
		\abs{\normFro{\cE}^2 - \sigma^2 \cdot n \cdot t}=\abs{\tr\left( \cal E^\top \id_{n\times n}\cal E\right) - \sigma^2 \cdot n \cdot t} &\le n^{c} \cdot \sigma^2 \| \id_{n\times n}\|_F \nonumber\\
		&= n^{1/2+c} \cdot \sigma^2 \le n^{-c_{\infty}} \cdot \sigma^2 \cdot n \cdot t, \label{eq_gA_err3}
	\end{align}
	as long as $c$ is sufficiently small. 
	For the inner product between $\cW A$ and $\cE$, we have that with high probability,
	\begin{align}
		\bigabs{\inner{\cW A}{\cE} - \sigma^2\cdot p \cdot r } &= \bigabs{\bigtr{\left(\cE^\top U_X U_X^{\top}\cE  - p\sigma^2 \cdot  \id_{t\times t} \right)  U_AU_A^{\top} }} \nonumber  \\
		&\le \bignormFro{U_{A} U_A^{\top}} \cdot \bignorm{\cE^\top U_X U_X^{\top} \cE - p \sigma^2 \cdot  \id_{t\times t}} \nonumber \\
		&\le \sqrt{r} \cdot (n^{\e}\cdot \sigma^2\cdot \|U_X U_X^\top\|_F) \nonumber \\
		&\le n^{1/2+c} \cdot \sigma^2 \cdot \sqrt{r}  \le  n^{-c_{\infty}} \cdot \sigma^2 \cdot n \cdot t ,\label{eq_gA_err4}
	\end{align}
as long as $c$ is sufficiently small. Here in the third step, we applied equation \eqref{vcalAE3} to $\bignorm{\cE^\top U_X U_X^{\top} \cE - p \sigma^2 \cdot  \id_{t\times t}}$ and used that $ \bignormFro{U_{A} U_A^{\top}}=\sqrt{r}$ because $U_A$ is of rank $r$. In the fourth step, we used that $\|U_X U_X^\top\|_F=\sqrt{p}\le \sqrt{n}$ because $U_X$ is of rank $p$.

%	\begin{align}
%		\bigabs{\inner{\cW A}{\cE} - \ex{\inner{\cW A}{\cE}}} &= \bigabs{\bigtr{U_X U_X^{\top} (\cE U_AU_A^{\top} \cE^{\top} - \sigma^2 \cdot r \id_{n\times n})}} \nonumber  \\
%		&\le \bignormFro{U_{X} U_X^{\top}} \cdot \bignorm{\cE U_A U_A^{\top} \cE^{\top} - \sigma^2 \cdot r \id_{n\times n}} \nonumber \\
%		&\le p^{1/2} \cdot (\sigma^2 r\cdot p^{\e}). \label{eq_gA_err4}
%	\end{align}
	%\begin{align*}
	%	%|\inner{U_X U_X^{\top} \bigbrace{\varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1}W_j}{\varepsilon_j}|
	%	\abs{W_i^{\top} (\cW\cW^{\top})^{-1} W_j \cdot \bigbrace{\varepsilon_i^{\top} U_X U_X^{\top} \varepsilon_j}}
	%	&\le |W_i^{\top} (\cW\cW^{\top})^{-1}W_j| \cdot \sigma^2 p^{\e} \bigtr{(U_X U_X^{\top})^2}^{1/2} \le \sigma^2 p^{1/2+\e}
  % &\left|\left(1-\mathop{\mathbb{E}}_{\varepsilon_j} \right)\left[\inner{U_X U_X^{\top} \bigbrace{\varepsilon_j W_j^{\top}} (\cW\cW^{\top})^{-1}W_j}{\varepsilon_j}\right]\right| \le |W_j^{\top} (\cW\cW^{\top})^{-1}W_j| \cdot \sigma^2 p^{\e} \tr \left[(U_X U_X^{\top})^2\right]\le \sigma^2 p^{1/2+\e},\\
  % &\left|\left(1-\mathop{\mathbb{E}}_{\varepsilon_j} \right)\left[\inner{U_X U_X^{\top} \bigbrace{\varepsilon_j W_j^{\top}} (\cW\cW^{\top})^{-1}W_j}{U_X U_X^{\top} \bigbrace{\varepsilon_j W_j^{\top}} (\cW\cW^{\top})^{-1}W_j}\right]\right|\\
  % &\le |W_j^{\top} (\cW\cW^{\top})^{-1}W_j|^2 \cdot \sigma^2 p^{\e} \tr \left[(U_X U_X^{\top})^4\right]\le \sigma^2 p^{1/2+\e},
	%\end{align*}
	%Combining equation \eqref{eq_gA_}, we get that with high probability
	%\begin{align}
	%	\left|g_2(\cal W)-\sigma^2(n\cdot t - p\cdot r)\right|=\left|g_2(\cal W)- \exarg{\varepsilon_1, \dots, \varepsilon_t} {g_2(\cal W)}\right| \lesssim \sigma^2 p^{1/2+\e}. \label{eq_gA_err}
	%\end{align}
	Combining equations \eqref{eq_gA_err1}, \eqref{eq_gA_err2}, \eqref{eq_gA_err3}, and \eqref{eq_gA_err4}, we obtain equation \eqref{eq_gA_err}.

>>>>

	We fill in missing details in the proof. Our first claim shows that the subspace spanned by the rows of $\hat{A}$ is close to that of $A^{\star}$.
	\begin{claim}\label{claim_opt_dist}
		Let $U_{\hat{A}} U_{\hat{A}}^{\top} \in\real^{t\times t}$ denote the subspace projection $\hat{A}^{\top} (\hat{A}\hat{A}^{\top})^{+} \hat{A}$.
		In the setting of Theorem \ref{thm_many_tasks}, we have that
		\[ \bignormFro{U_{\hat{A}} U_{\hat{A}}^{\top} - A^{\star} {A^{\star}}^{\top}}^2
				\le  n^{-c_{\varphi}} \cdot \frac{t(  \bignorm{\Sigma^{1/2} B^{\star}}^2 +  \sigma^2 )}{\lambda_r({B^{\star}}^{\top}\Sigma B^{\star})- \lambda_{r+1}({B^{\star}}^{\top}\Sigma B^{\star})}. \]
	\end{claim}
	The proof of the above claim is based on the following characterization.

@@

	The next piece of our proof deals with the prediction loss of hard parameter sharing.
	\begin{claim}\label{claim_pred_err}
		In the setting of Theorem \ref{thm_many_tasks},
		let $\hat{a}_i = \hat{A}^{\top} (\hat{A}\hat{A}^{\top})^{+} \hat{A}_i$.
		We have that the prediction loss of $\hat{\beta}_i^{\MTL} := \hat{B} \hat{A}_i$ satisfies that
		\begin{align*}
			\bigabs{L(\hat{\beta}_i^{\MTL}) - L(B^{\star} \hat{a}_i) - \sigma^2 \norm{\hat{a}_i}^2 \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}}
			\le  n^{-1/4} \left(L(B^{\star} \hat{a}_i) + \sigma^2  \cdot\|\hat a_i\|^2\right) .
		\end{align*}
	\end{claim}
	%The proof of Claim \ref{claim_opt_dist}, Claim \ref{lem_exp_opt}, and Claim \ref{claim_pred_err} can be found in Appendix \ref{app_proof_error_same_cov}.
	Provided with these results, we are ready to prove Theorem \ref{thm_many_tasks}.
	\begin{proof}[Proof of Theorem \ref{thm_many_tasks}]
		Using Claim \ref{claim_pred_err}, we get that the prediction loss of $\hat{\beta}_i^{\MTL}$ is equal to  $L(B^{\star}\hat{a}_i)+\sigma^2\norm{\hat{a}_i}^2\cdot \bigtr{\Sigma(X^{\top}X)^{-1}}$ up to a small enough error. Moreover, Claim \ref{claim_opt_dist} gives directly an upper bound on $\|\hat a_i - a_i^\star\|^2$. With this estimate, we can bound the difference
		$$L(B^{\star}\hat{a}_i)+\sigma^2\norm{\hat{a}_i}^2\cdot \bigtr{\Sigma(X^{\top}X)^{-1}} - L(B^{\star} {a}^\star_i)-\sigma^2\norm{{a}^\star_i}^2\cdot \bigtr{\Sigma(X^{\top}X)^{-1}}.$$
		Combined together, our proof is complete.
%		For the latter, we use Claim \ref{claim_opt_dist} to upper bound the difference between $\norm{\hat{a}_i}^2$ and $\norm{a_i^{\star}}^2$.
%		For $L(B^{\star}\hat{a}_i)$, we again use Claim \ref{claim_opt_dist} to upper bound the distance between $\hat{a}_i$ and $a_i^{\star}$.
%		Combined together, our proof is complete.
	\end{proof}

@@

	\paragraph{Part 3:} The last part is the square of $E_j$:
	\begin{align}\label{eq_gA_p3}
		\sum_{j=1}^t \norm{E_j}^2 &= \bignormFro{\cW A - \cE}^2
		= \bignormFro{\cE}^2 - \inner{\cW A}{\cE},
	\end{align}
	where in the second step we use $\norm{\cW A}^2 = \inner{\cW A}{\cE}$ by algebraic calculation.
	Hence, it suffices to show that the expectation of equation \eqref{eq_gA_p3} is equal to $\sigma^2 (n\cdot t - p\cdot r)$.
	First, we have that $\ex{\|\cE\|_F^2} = \sigma^2 \cdot n \cdot t$.
%	Conditional on $X$, we have that
%	\begin{align*}
%		\exarg{\cE}{\norm{E_j}^2}
%		= \exarg{\cE}{\sum_{j=1}^t \bigbrace{\bignorm{\cW A_j}^2 - 2\inner{\cW A_j}{\varepsilon^{(j)}} }} + \sigma^2 \cdot n \cdot t.
%	\end{align*}
%	We consider both terms in the above equation one by one.
	Second, we show that
	%	\begin{align*}
	%		\inner{\cW A}{\cE} = \sigma^2 \cdot r \cdot \bigtr{U_X U_X^{\top}} = \sigma^2 \cdot r \cdot p,
	%	\end{align*}
	%because $U_X$ has rank $p$ by Fact \ref{lem_minv}.
	\begin{align*}
		\exarg{\cE}{ \inner{\cW A}{\cE}} =\exarg{\cE}{\bigtr{\cal E^\top U_X U_X^\top \cal E U_AU_A^\top} }= p\sigma^2 \cdot \bigtr{ U_AU_A^\top} =  p \sigma^2 \cdot r,
	\end{align*}
	where $U_XU_X^\top = X(X^{\top} X)^{-1} X^{\top}$.
	The first step follows by applying the definition of $\cW$.
	The last step is because $U_AU_A^\top$ has rank $r$.
	Hence, it suffices to show the second step is correct.
	For any $1\le i, j \le t$, let $\delta_{i, j} = 1$ if $i = j$, and $0$ otherwise.
	%\begin{align}
	%	\sum_{j=1}^t \norm{\cW A_j}^2 = \sum_{j=1}^t \bigtr{\cW A_j A_j^{\top} \cW^{\top}} = \bigtr{\cW AA^{\top} \cW^{\top}} = \bigtr{U_X U_X^{\top} \cE A^{\top} (AA^{\top})^{-1} A \cE^{\top}}. \label{eq_proof_same_cov_1}
	%\end{align}
	%We observe that
	Because $\varepsilon^{(i)}$ and $\varepsilon^{(j)}$ are pairwise independent, we have that
	\begin{align*}
			 \exarg{\cE}{(\cE^{\top}U_XU_X^\top \cE)_{ij} }
		&= \exarg{\cE}{{\varepsilon^{(i)}}^\top U_X U_X^\top  \varepsilon^{(j)} } = \sigma^2 \cdot \tr\left[U_XU_X^\top \right] \cdot \delta_{ij} = p\sigma^2 \cdot \delta_{ij}.
	\end{align*}
	The last step uses the fact that $\tr[U_XU_X^\top] = p$.
	Hence, the second step is correct.
	%Above, the second step used the fact that $\E(\varepsilon^{(i)}_k \varepsilon^{(i)}_l )=\sigma^2\cdot \delta_{ij}\delta_{kl}$ for $1\le k,l \le n$, and the third step used the fact that $\tr(U_XU_X^\top) =\tr(U_X^\top U_X) =p$.
	%Next, note that
	%\[ \sum_{j=1}^t \inner{\cW A_j}{\varepsilon^{(j)}} = \bigtr{\cW A\cE^{\top}}, \]
	%which is equal to equation \eqref{eq_proof_same_cov_1} by the definition of $\cW$.

	Combining the three parts, the proof is complete.
	\end{proof}

@@

	\begin{proof}[Proof of Claim \ref{claim_opt_dist}]
	Corresponding to the right-hand side of \eqref{eq_gA}, we define the function
	\be\label{same_hA}h(A):= n \bignormFro{\Sigma^{1/2} B^{\star} \bigbrace{A^{\top} (AA^{\top})^{+} A - \id_{t\times t}}}^2 + \sigma^2 (n\cdot t - p \cdot r).\ee
	Let $\e$ be a fixed constant that is sufficiently small.
	Let $c_{\infty}$ be any fixed value within $(0, 1/2 - \e)$.
	To show that $U_{\hat{A}}U_{\hat{A}}^\top$ is close to $A^\star {A^\star}^\top$, we first show that $g(A)$ is close to $h(A)$ as follows:
	\begin{align}\label{eq_gA_err}
		\bigabs{g(A) - h(A)} \lesssim  n^{-c_{\varphi}} \cdot n \bignorm{\Sigma^{1/2} B^{\star} (U_AU_A^{\top} - \id_{t\times t})}_F^2 + n^{-c_{\infty}} \cdot \sigma^2 \cdot n \cdot t.
	\end{align}
%	\begin{align}\label{eq_gA_err}
%		\bigabs{g(A) - \exarg{\cE, X}{g(A)}} \lesssim p^{-c_{\varphi}} \cdot n \bignorm{\Sigma^{1/2} B^{\star} (U_AU_A^{\top} - \id)}^2 + p^{-c_{\infty}} \cdot \sigma^2 \cdot n \cdot t.
%	\end{align}
	We consider the concentration error of each part of $g(A)$.

	For equation \eqref{eq_gA_p1}, % $g_0(\cal W)= \sum_{j=1}^t\left\|Z v_j \right\|^2$.
%	$$g_0(\cal W)= \sum_{j=1}^t\left\|Z v_j \right\|^2,\quad v_j:= \Sigma^{1/2}\left(B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j -  \beta_j\right).$$
%	note that $X H_j = Z \Sigma^{1/2} H_j \in \real^n$ is a random vector with i.i.d. entries of mean zero, variance $\|\Sigma^{1/2}H_j\|^2$, and finite $\varphi$-th moment by Assumption \eqref{assume_rm}.
%	Hence by the law of large numbers, we have that with high probability	
	applying Corollary \ref{cor_largedeviation} to $X H_j = Z \Sigma^{1/2} H_j$, we obtain that 
	${\left\|Z \Sigma^{1/2} H_j \right\|^2 } = { n \|\Sigma^{1/2} H_j\|^2} \cdot (1 + \OO(n^{-c_\varphi}))$ with high probability. 
	This implies that
	\begin{align}
		\abs{\sum_{j=1}^t \|X H_j\|^2 -  \sum_{j=1}^t n\norm{\Sigma^{1/2} H_j}^2} \lesssim   n^{-c_{\varphi}} \cdot n  \bignorm{\Sigma^{1/2} B^{\star} (U_{A}U_A^{\top} - \id_{t\times t})}^2. \label{eq_gA_err1}
	\end{align}

	For equation \eqref{eq_gA_p2}, 
	%using Lemma \ref{largedeviation} in Appendix \ref{app_tool} and the fact that all moments of $\varepsilon_i$ exist by Assumption \eqref{assmAhigh2}, 
	using Corollary \ref{cor_calE}, we obtain the following with high probability:
	\begin{align}
		|\inner{XB^{\star} (U_AU_A^{\top} - \id_{t\times t})}{\cE}| &\le n^\e \cdot \sigma \cdot \bignormFro{XB^{\star} (U_AU_A^{\top} - \id_{t\times t})} \nonumber \\
		&\le n^{\e} \cdot \sigma \cdot \norm{Z} \cdot \bignormFro{\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id_{t\times t})} \nonumber \\
		&\lesssim n^{\e} \cdot \sigma \cdot \sqrt{n} \bignorm{\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id_{t\times t})} \label{eq_gA_err2}
%		&\le  n^{c_\infty +c} \cdot \bignorm{\Sigma^{1/2} B^{\star} (U_AU_A^{\top} - \id_{t\times t})}^2 + n^{-c_{\infty}} \cdot \sigma^2 \cdot n \cdot t.
	\end{align}
	In the second step, we use the fact that $X=Z\Sigma^{1/2}$.
	In the third step, we use Fact \ref{fact_minv}(ii) to bound the operator norm of $Z$ by $\OO(\sqrt{n})$, and use $\bignormFro{\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id_{t\times t})}\le \sqrt{t} \bignorm{\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id_{t\times t})}$ since the matrix $\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id_{t\times t})$ has rank at most $t$.
	By the AM-GM inequality, equation \eqref{eq_gA_err2} is bounded by the right-hand side of \eqref{eq_gA_err}.

	For equation \eqref{eq_gA_p3}, using Corollary \ref{cor_calE},
	%Lemma \ref{largedeviation} and the fact that all moments of $\varepsilon_i$ exist, 
	we obtain that with high probability,
	\begin{align}
		\abs{\normFro{\cE}^2 - \sigma^2 \cdot n \cdot t}=\abs{\tr\left[ \cal E^\top \id_{n\times n}\cal E\right] - \sigma^2 \cdot n \cdot t} &\le n^{c} \cdot \sigma^2 \| \id_{n\times n}\|_F \nonumber\\
		&= n^{1/2+c} \cdot \sigma^2 \le n^{-c_{\infty}} \cdot \sigma^2 \cdot n \cdot t. \label{eq_gA_err3}
	\end{align}
	For the inner product between $\cW A$ and $\cE$, we have that with high probability,
	\begin{align}
		\bigabs{\inner{\cW A}{\cE} - \sigma^2\cdot p \cdot r } &= \bigabs{\bigtr{\left(\cE^\top U_X U_X^{\top}\cE  - p\sigma^2 \cdot  \id_{t\times t} \right)  U_AU_A^{\top} }} \nonumber  \\
		&\le \bignormFro{U_{A} U_A^{\top}} \cdot \bignorm{\cE^\top U_X U_X^{\top} \cE - p \sigma^2 \cdot  \id_{t\times t}} \nonumber \\
		&\le \sqrt{r} \cdot n^{\e}\cdot \sigma^2\cdot \|U_X U_X^\top\|_F \nonumber \\
		&\le n^{1/2+c} \cdot \sigma^2 \cdot \sqrt{r}  \le  n^{-c_{\infty}} \cdot \sigma^2 \cdot n \cdot t.\label{eq_gA_err4}
	\end{align}
	Here in the third step, we apply equation \eqref{vcalAE3} to $\bignorm{\cE^\top U_X U_X^{\top} \cE - p \sigma^2 \cdot  \id_{t\times t}}$ and use that $ \bignormFro{U_{A} U_A^{\top}}=\sqrt{r}$ because $U_A$ has rank $r$. In the fourth step, we use $\|U_X U_X^\top\|_F=\sqrt{p}$ because $U_X$ has rank $p$.

	Combining equations \eqref{eq_gA_err1}, \eqref{eq_gA_err2}, \eqref{eq_gA_err3}, and \eqref{eq_gA_err4}, we obtain equation \eqref{eq_gA_err}.
